\chapter{Obtaining and Installing Utilities for Mass Spectrometry Analysis of Proteins}

\section{Obtaining Utilities for Mass Spectrometry Analysis of Proteins}

UMSAP is distributed free of charge for anyone interested in using it. To obtain
a copy of the software just register at \href{https://www.umsap.nl}{www.umsap.nl}
and go to the Download page.

No extra software or packages are needed for UMSAP to properly work.

So far, UMSAP have been tested in macOS \num[parse-numbers=false]{10.12.6} and
\num[parse-numbers=false]{10.14.6} and Windows \num{10}.
Linux users may download the source code of the software and adapt it to their
specific distribution of Linux. Support for some Linux distributions will be
available in the future.

\section{Installing Utilities for Mass Spectrometry Analysis of Proteins}

\textit{\textbf{Windows}}

Unzip the file you just downloaded from \href{https://www.umsap.nl}{www.umsap.nl}.
Then, copy the folder UMSAP to the location in your file system where you want
to keep it. Finally, create a shortcut to the executable file UMSAP.exe found
inside the main folder UMSAP. That is all. You are now ready to use UMSAP.

\textit{\textbf{macOS}}

Unzip the file you just downloaded from \href{https://www.umsap.nl}{www.umsap.nl}.
Then, just move the UMSAP.app folder to /Applications/. That is all. You are now
ready to use UMSAP. 

Depending on the security settings in macOS, it may be needed to explicitly allow
UMSAP to be opened the first time the app is used.

\section{Uninstalling Utilities for Mass Spectrometry Analysis of Proteins}

UMSAP will not create any installation file in your computer. Therefore, the only
thing you need to do, to completely uninstall UMSAP, is to delete the folder
UMSAP.app in macOS or UMSAP in Windows. You should also delete any shortcut
pointing to the executable file of UMSAP and the configuration file
.umsap\_config.json in your home folder. That is all.